%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\newcommand{\ts}{\textsuperscript}
\usepackage{mathtools}


\usepackage[backend=biber]{biblatex}
\addbibresource{qlu_pub.bib}

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Qihong}{Lu}
% \title{Resumé title}                               % optional, remove / comment the line if not wanted
% \address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(608)~335~2451}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
% \phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{qihong.lu@wisc.edu}                               % optional, remove / comment the line if not wanted
% \homepage{qihongl.github.io}                         % optional, remove / comment the line if not wanted

\extrainfo{
Personal Page: \href{https://qihongl.github.io/}{https://qihongl.github.io/}
\\
Github Page: \href{https://github.com/QihongL}{https://github.com/QihongL}
}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2013--2017}{B.S.}{}{University of Wisconsin-Madison}{Madison, WI, U.S.A.}{Major in Psychology \& Mathematics, Minor in Computer Science \\Comprehensive Honors\\Psi Chi, Phi Beta Kappa as a junior}  


\section{Research Experience}
\cventry{Summer 2013}{Research Intern}{}{Laboratory of Neural Coding}{}{P.I.: Dr. Longnian Lin, Shanghai Key Laboratory of Brain Functional Genomics
}
\cventry{2013-2015}{Research Assistant}{}{Language and Cognitive Neuroscience Lab}{}{P.I.: Dr. Maryellen MacDonald \& Dr. Mark Seidenberg, UW-Madison
}
\cventry{2014-present}{Research Assistant}{}{Knowledge and Concepts Lab}{}{P.I.: Dr. Timothy Rogers, UW-Madison
}
\cventry{Summer 2015 \& 2016}{Visiting Researcher}{}{The Parallel Distributed Processing Lab}{}{P.I.: Dr. James McClelland, Stanford University
}


\section{Extracurricular Activities}
\cventry{2013-2014}{Tutor}{}{Greater University Tutoring Service}{}{
\begin{itemize}%
\item Taught Calculus I/II and Introductory Biology.
\end{itemize}
}

\cventry{2013-2014}{Social Science Chair}{}{$\text{IV}\cdot\Omega$ Academic Society}{}{
\begin{itemize}%
\item Organized social science mini-lectures; presented recent advances in social science.
\end{itemize}
}

\cventry{2014-present}{Student Representative}{}{Letter \& Science Faculty Honors Committee}{}{
\begin{itemize}%
\item Discussing and revising academic policies and curriculum.
\item Reviewing scholarship and research grant applications for undergraduate students.
\end{itemize}
}


\section{Honors \& Awards}
\cventry{2014, 2015}{Undergraduate Research Scholar Award}{}{Psychology Department}{}{Nominated by Dr.Maryellen MacDonald \& Dr.Timothy Rogers}
\cventry{2014}{International Undergraduate Writing Contest 3\ts{rd} Place}{}{English Department}{}{}
\cventry{2014}{Welton Summer Sophomore Research Grant}{}{}{L\&S Honors Program}{}
\cventry{2014}{Margaret and Allard Smith Scholarship}{}{}{College of L\&S}{High achieving 2\ts{nd} year student}
\cventry{2015}{Hilldale Undergraduate Research Fellowship}{}{}{College of L\&S}{}
\cventry{2015}{Bromley Research Conference Travel Grant}{}{}{L\&S Honors Program}{}
\cventry{2015}{CSLI Summer Research Internship}{}{}{Stanford University}{}
\cventry{2016}{David H. Durra Scholarship}{}{}{College of L\&S}{High achieving student in mathematics.}
\cventry{2016}{Undergraduate Travel Awards}{}{}{L\&S Honors Program}{}



\section{Technical Skills}
\cvitem{Advanced}{Matlab, Python, Java, GitHub}
\cvitem{Intermediate}{R, LENS, SPSS, Linux, \LaTeX}

\section{Professional Affiliation}
\cvitem{2014-present}{Cognitive Neuroscience Society}
\cvitem{2015-present}{Cognitive Science Society}

\section{Papers}
\hangindent=0.7cm
\textbf{Lu, Q.}, Cox, C., Rogers, T. T., Lambon Ralph, M., \& Takahashi R. (manuscript in preparation). An interactive account for human vision: a recurrent neural network explains neural and behavioral temporal dynamics of object recognition processes.

\hangindent=0.7cm
McClelland, J.L., Mickey, K., Hansen S., \& \textbf{Lu, Q.} (manuscript in preparation). A Parallel-Distributed Processing approach to mathematical cognition. 

\hangindent=0.7cm
Wang, T., \textbf{Lu, Q.} \& Seidenberg, M.S. (manuscript in preparation). The role of transitional probability in reading Chinese. 


\section{Posters}
\hangindent=0.7cm
Cox, C. R., \textbf{Lu, Q.}, \& Rogers, T. T. (2015). Iterative Lasso: An even-handed approach to whole brain multivariate pattern analysis. Poster presented at the 22\ts{nd} Cognitive Neuroscience Society annual conference, San Francisco, CA.

\hangindent=0.7cm
Cox, C. R., \textbf{Lu, Q.}, \& Rogers, T. T. (2015). Iterative Lasso: An even-handed approach to whole brain multivariate pattern analysis. Poster presented at the Neuroimaging, Computational Neuroscience and Neuroengineering Workshop, Madison, WI.

\hangindent=0.7cm
\textbf{Lu, Q.}, \& Rogers, T. T. (2016). An interactive model accounts for both ultra-rapid superordinate classification and basic-level advantage in object recognition. Poster to be presented at the 38\ts{th} Annual Meeting of the Cognitive Science Society, Philadelphia, PA.

\hangindent=0.7cm
\textbf{Lu, Q.}, \& McClelland, J.L. (2016). Teaching a neural network to count: reinforcement learning with ``social scaffolding''. Poster to be presented at the 15\ts{th} Neural Computation and Psychology Workshop, Philadelphia, PA.


\section{Talks}
\hangindent=0.7cm
\textbf{Lu, Q.}, \& Rogers, T. T. (2015). Modeling the temporal dynamics of human categorization behavior. Talk delivered at UW-Madison Undergraduate Research Symposium, Madison, WI.

\hangindent=0.7cm
\textbf{Lu, Q.}, \& McClelland, J.L. (2015). Teaching a PDP model to count. Talk delivered at Stanford Center of Study of Language and Information Summer Research Program Final Presentation, Stanford, CA. 

\hangindent=0.7cm
\textbf{Lu, Q.}, \& Rogers, T. T. (2016). A recurrent neural network for object recognition. Talk delivered at UW-Madison Senior Honors Thesis Symposium, Madison, WI.


\section{Online Course Certificates}
\cventry{2013}{Model Thinking}{Coursera}{}{University of Michigan}{}
\cventry{2013}{Behavioral Economics in Action}{edX}{}{University of Toronto}{}
\cventry{2014}{Fundamentals of Neuroscience I}{edX}{}{Harvard University}{}
\cventry{2014}{Introduction to Dynamical System and Chaos}{}{Santa Fe Institute}{}{}
\cventry{2014}{Moralities of Everyday Life}{Coursera}{}{Yale University}{}
\cventry{2014}{Statistical Analysis of fMRI Data}{Coursera}{}{Johns Hopkins University}{}
\cventry{2014}{Introduction to Complexity}{}{}{Santa Fe Institute}{}
\cventry{2014}{Justice}{edX}{}{Harvard University}{}
\cventry{2014}{Machine Learning}{Coursera}{}{Stanford University}{}
\cventry{2014}{Intro to Computer Science \& Programming Using Python}{Coursera}{}{MIT}{}
\cventry{2015}{The Brain and Space}{Coursera}{}{Duke University}{}
\cventry{2016}{Statistical Learning}{Stanford Online}{}{Stanford University}{}
\cventry{2016}{Build a Computer from 1\ts{st} Principles}{Coursera}{}{Hebrew University of Jerusalem}{
\begin{flushright}
(Certificates available upon request)
\end{flushright}
}



\end{document}


%% end of file `template.tex'.
